The Strong Gravitational Lens Finding Challenge

### 2017-09-08 paper.tex
Edit.
Update on Overleaf.

\title[SL Challenge]{The Strong Gravitational  Lens Finding Challenge}
%C.~E.~Petrillo$^{1}$,  C.~Tortora$^{1}$, L.~V.~E.~Koopmans$^{1}$, \and G.~Verdoes~Kleijn$^{1}$
\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
M. Meneghetti,$^4$ 
Camille Avestruz,$^{11,12,13,\dagger}$
\newauthor
Fabio Bellagamba,$^1$
Cl\'ecio R. Bom,$^{18,19}$
Emmanuel Bertin,$^3$ 
\newauthor
R\'emi Cabanac,$^2$ 
Etienne Decenci\`ere,$^{10}$
R\'emi Flamary,$^8$
\newauthor
Raphael Gavazzi,$^{17}$ 
Mario Geiger,$^6$ 
Philippa Hartley,$^7$
\newauthor
Marc Huertas-Company,$^9$
Neal Jackson,$^7$ 
Eric Jullo,$^{16}$
\newauthor
Gijs Verdoes Kleijn,$^{22}$ 
Jean-Paul Kneib,$^6$
Leon Koopmans,$^{22}$
\newauthor
Fran\c{c}ois Lanusse,$^{20}$ 
Chun-Liang Li,$^{21}$
Quanbin Ma,$^{21}$ 
\newauthor
Martin Makler,$^{19}$
Nan Li,$^{14}$
Matthew Lightman,$^{15}$
\newauthor
Carlo Enrico Petrillo,$^{22}$
Christoph Sch\"{a}fer,$^6$ 
Alessandro Sonnenfeld,$^5$ 
\newauthor
Amit Tagore,$^7$
Crescenzo Tortora,$^{22}$
Diego Tuccillo,$^{9,10}$
\newauthor
Manuel B. Valent\'in,$^{19}$
and Santiago Velasco-Forero,$^{10}$
\\
% List of institutions
$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
$^{2}$ IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.\\
$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  \\ 98bis Bd Arago, F-75014, Paris France.\\
$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
$^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{6}$ \red{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)
Observatoire de Sauverny CH - 1290 Versoix Switzerland} \\
$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of \\ Manchester, Oxford Rd, Manchester M13 9PL, UK \\
$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique,\\ Observatoire de la C\^{o}te d'Azur, Parc Valrose, 06108 Nice, France \\
$^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
$^{10}$ MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue \\ Saint-Honore, Fontainebleau, France \\
$^{11}${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{12}${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{13}${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{14}${School of Physics and Astronomy, Nottingham University, University Park, Nottingham, NG7 2RD, UK
}\\
$^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
$^{16}$\red{ LAM - Laboratory of Astrophysics of Marseille P\^ole de l'\'Etoile Website of Ch\^ateau-Gombert 
38,} \\ \red{rue Fr\'ed\'eric Joliot-Curie 13388 Marseille cedex 13 FRANCE} \\
$^{17}$\red{Institut d'Astrophysique de Paris (IAP)- 98 bis boulevard Arago - 75014 Paris } \\
$^{18}${Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil}\\
$^{19}${Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil}\\
$^{20}${McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
$^{21}${School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
$^{22}${Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands}\\
$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
}

@@

These are methods that classify the objects by making linear or nonlinear boundaries in a feature space.  The features are properties of the image and are typically chosen by the user with a combination of knowledge, intuition and trial-and-error.  Using the training set, an optimal boundaries are found according to a criterion that depends on the method.  The machine learns which combinations of features are best for distinguishing between lenses and non-lenses.

\red{Philippa, what do you think of this? }

>>>>

\title[SL Challenge]{The Strong Gravitational  Lens Finding Challenge}
%C.~E.~Petrillo$^{1}$,  C.~Tortora$^{1}$, L.~V.~E.~Koopmans$^{1}$, \and G.~Verdoes~Kleijn$^{1}$
\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
M. Meneghetti,$^4$ 
Camille Avestruz,$^{11,12,13,\dagger}$
\newauthor
Fabio Bellagamba,$^1$
Cl\'ecio R. Bom,$^{18,19}$
Emmanuel Bertin,$^3$ 
\newauthor
R\'emi Cabanac,$^2$ 
Etienne Decenci\`ere,$^{10}$
R\'emi Flamary,$^8$
\newauthor
Raphael Gavazzi,$^{17}$ 
Mario Geiger,$^6$ 
Philippa Hartley,$^7$
\newauthor
Marc Huertas-Company,$^9$
Neal Jackson,$^7$ 
Eric Jullo,$^{16}$
\newauthor
Gijs Verdoes Kleijn,$^{22}$ 
Jean-Paul Kneib,$^6$
Leon Koopmans,$^{22}$
\newauthor
Fran\c{c}ois Lanusse,$^{20}$ 
Chun-Liang Li,$^{21}$
Quanbin Ma,$^{21}$ 
\newauthor
Martin Makler,$^{19}$
Nan Li,$^{14}$
Matthew Lightman,$^{15}$
\newauthor
Carlo Enrico Petrillo,$^{22}$
Christoph Sch\"{a}fer,$^6$ 
Alessandro Sonnenfeld,$^5$ 
\newauthor
Amit Tagore,$^7$
Crescenzo Tortora,$^{22}$
Diego Tuccillo,$^{9,10}$
\newauthor
Manuel B. Valent\'in,$^{19}$
and Santiago Velasco-Forero,$^{10}$
\\
% List of institutions
\vspace{0.5cm}\\
$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
$^{2}$ IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.\\
$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  \\ 98bis Bd Arago, F-75014, Paris France.\\
$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
$^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{6}$ \red{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)
Observatoire de Sauverny CH - 1290 Versoix Switzerland} \\
$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of \\ Manchester, Oxford Rd, Manchester M13 9PL, UK \\
$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique,\\ Observatoire de la C\^{o}te d'Azur, Parc Valrose, 06108 Nice, France \\
$^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
$^{10}$ MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue \\ Saint-Honore, Fontainebleau, France \\
$^{11}${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{12}${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{13}${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^{14}${School of Physics and Astronomy, Nottingham University, University Park, Nottingham, NG7 2RD, UK
}\\
$^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
$^{16}$\red{ LAM - Laboratory of Astrophysics of Marseille P\^ole de l'\'Etoile Website of Ch\^ateau-Gombert 
38,} \\ \red{rue Fr\'ed\'eric Joliot-Curie 13388 Marseille cedex 13 FRANCE} \\
$^{17}$\red{Institut d'Astrophysique de Paris (IAP)- 98 bis boulevard Arago - 75014 Paris } \\
$^{18}${Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil}\\
$^{19}${Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil}\\
$^{20}${McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
$^{21}${School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
$^{22}${Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands}\\
$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
}

@@

These are methods that classify the objects by making linear or nonlinear boundaries in a feature space.  The features are properties of the image and are typically chosen by the user with a combination of knowledge, intuition and trial-and-error.  Using the training set, an optimal boundaries are found according to a criterion that depends on the method.  The machine learns how to weight the features best for distinguishing between lenses and non-lenses.
